Analysis of Turkey's Trade with Selected Countries

### 2018-12-23 Final/PresentationFinal.Rmd
.

```{r, include=FALSE, message=FALSE, warning=FALSE}
library(shiny)
library(tidyverse)
library(dplyr)
library(readxl)
library(leaflet)
library(reshape2)
library(gridExtra)
library(lubridate)
library(plotrix)
library(treemap)
```

@@

## Analysis | K-Means Clustering

@@

>>>>

```{r, include=FALSE, message=FALSE, warning=FALSE}
library(shiny)
library(tidyverse)
library(dplyr)
library(readxl)
library(leaflet)
library(reshape2)
library(gridExtra)
library(lubridate)
library(plotrix)
library(treemap)
library(cluster)
library(factoextra)
```

@@

## K-Means Clustering | Determining Optimal Cluster

```{r, fig.align="center"}
product_year<-export_Product_Group %>%
filter(Export_Value > 0) %>%
group_by(Product_Group_Name,year)%>%
summarise(Adet=n(), Toplam = sum(Export_Value))

product_Cluster <-dcast(product_year, Product_Group_Name ~ year , value.var = "Toplam") %>%
   rename(Toplam_2013 = "2013") %>%
   rename(Toplam_2014 = "2014") %>%
   rename(Toplam_2015 = "2015") %>%
   rename(Toplam_2016 = "2016") %>%
   rename(Toplam_2017 = "2017")

product_Cluster2 <- product_Cluster[,-1]
rownames(product_Cluster2) <- substr(product_Cluster$Product_Group_Name, start=1, stop=47)

#Scale the values

product_Cluster2 <- scale(product_Cluster2)

#head(product_Cluster2)

# Create distance matrix
distance <- get_dist(product_Cluster2)
#fviz_dist(distance, gradient = list(low = "#00AFBB", mid = "white", high = "#FC4E07"))

#Determine optimal cluster with Elbow Method
set.seed(11)
Elbow <- fviz_nbclust(product_Cluster2, kmeans, method = "wss")

#Determine Optimal Cluster with Silhoutte Method
Silhoutte <- fviz_nbclust(product_Cluster2, kmeans, method = "silhouette")

#Determine Optimal Cluster with Gap Statistics Method
set.seed(12)
gap_stat <- clusGap(product_Cluster2, FUN = kmeans, nstart = 25, K.max = 10, B = 50)
GapStat <- fviz_gap_stat(gap_stat)

grid.arrange(Elbow, Silhoutte, GapStat, nrow = 1)

## K-Means Clustering | Computing K-Means

```{r, fig.align="center"}

# Compute k-means with 2,3 and 4 clusters 
k1 <- kmeans(product_Cluster2, centers = 2, nstart = 25)
k2 <- kmeans(product_Cluster2, centers = 3, nstart = 25)
k3 <- kmeans(product_Cluster2, centers = 4, nstart = 25)

#print (k3)

k1p <- fviz_cluster(k1, data = product_Cluster2, geom = "point") + ggtitle("k = 2")
k2p <- fviz_cluster(k2, data = product_Cluster2, geom = "point") + ggtitle("k = 3")
k3p <- fviz_cluster(k3, data = product_Cluster2, geom = "point") + ggtitle("k = 4")

grid.arrange(k1p, k2p, k3p, nrow = 3)

## K-Means Clustering | Computing K-Means

```{r, fig.align="center"}

fviz_cluster(k3, data = product_Cluster2) + ggtitle("k = 4")

@@

As a result of descriptive analysis of Turkey's trade with G7 countries besides India, China and Russia, we noted that;

* Turkeys’ biggest trade partners are China, Germany, Russia and US at import side while they are Germany, UK, Italy and USA at export side. 
* Germany and USA are the 2 top countries seen in both directions of trade.
* Generally we have fluctuated trade trend with Russia.
* Turkey's trade deficit analyisis gives the results : 
  + UK gives trade surplus for all years analysed 
  + China, Russia, Germany and USA have the most significant effect on trade deficit
  + Trade deficit has negatively correlated with USD/TL rate between 2013 and 2016 but there is no relation BIST100 index.
  + Turkey's trade deficit comes from China, Russia, Germany countires and most of deficit comes from products below :
      + Electrical machinery, equipments and machinery, mechanical appliances
      + Mineral fuels, mineral oils and products of their distillation constitute 
      + Vehicles other than railway and mechanical and electronical machinery and equipments

* As a result of clustering exported products;
  + Vehicles other than railway is the group we spent the most money
  + Second group consist of Machinery, mechanical appliances, electronical machinery- equipments and clothing while third one includes iron, steel, pearls, ores etc.

## Thanks - Q & A

![](C:\Users\emrek\Google Drive\BDA\503-EssentialsOfDataAnalytics\GitHub\gpj18-group_four\images\4logo.png)

For the full report and workpapers, please refer to [Group Fou*R* GitHub Pages](https://mef-bda503.github.io/gpj18-group_four/)
